There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-10 paper/icml_drau/advup.tex
Advances.

%! TEX root = icml_drau.tex
\section{Reinforcement learning with a continuous time limit}
As seen in Sec.~\ref{sec:framework}, there is no continuous time limit to
Q-learning. In continuous time, $Q^\pi$ is independant of actions and can thus
not be used to select promising actions.  In near continuous time, $Q^\pi$
still depends on actions, and can still be used to choose promising actions
under the current policy. However, when approximating $Q^\pi$, if the
approximation error is much bigger than $\bigO(\deltat)$, approximation errors
dominates, and the hierarchy of actions given by the approximation is likely to
be erroneous.
When the approximate Q-function is initialized, if the effect of actions on the
Q-function is order of magnitudes higher than what it should be, approximating
$Q^\pi$ is likely to be difficult. Besides, the error is likely to be further
propagated when the equation used to update our approximate $Q$ function
relies on bootstraping, as is the case for usual temporal difference derived methods.

\subsection{Reparameterizing $Q_\theta$}
\label{subsec:reparam}
To prevent overestimating the dependency on actions of the approximation of
$Q^\pi$, $Q_\theta$, in an environment with time discretization $\deltat$,
Eq.~\eqref{eq:reparam_q_pi} naturally yields the following reparameterization
\begin{equation}
	Q_\theta(s, a) = V_{\theta_1}(s) + \deltat A_{\theta_2}(s, a).
\end{equation}
To avoid cumbersome notations, in what follows, parameter indices are dropped.
The insight behind this parameterization is that when $Q$ correctly
approximates $Q^\pi$, $V$ should approximate the value function, while $A$
should approximate the advantage function, as defined in Eq.~\eqref{eq:adv}.

The proposed reparameterization does not, on its own, guarantee that
when $Q$ correctly approximates $Q^\pi$, $A$ approximates $A^\pi$.  Indeed, for
any given pair $V$, $A$, the transformed pair
\begin{align}
	\tilde{V}(s) &= V(s) - f(s)\\
	\tilde{A}(s, a) &= A(s, a) + \frac{f(s)}{\deltat}
\end{align}
yields the exact same $Q$ function. Consequently, $Q$ can correctly approximate
$Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce, identifiability of $A$, one must enforce that 
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q^\pi = Q$,
\begin{align}
	A^\pi(s, a) &= \frac{Q^\pi(s,a) - V^\pi(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}\\
		    &= A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by writing $A$ as
\begin{equation}
	A(s, a) = \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}

>>>>

%! TEX root = icml_drau.tex
\section{Reinforcement learning with a continuous time limit}
As seen in Sec.~\ref{sec:framework}, there is no continuous time limit to
Q-learning. In continuous time, $Q^\pi$ is independant of actions and can thus
not be used to select promising actions.  In near continuous time, $Q^\pi_\deltat$
still depends on actions, and can still be used to choose promising actions
under the current policy. However, when approximating $Q^\pi_\deltat$, if the
approximation error is much bigger than $\bigO(\deltat)$, approximation errors
dominates, and the hierarchy of actions given by the approximation is likely to
be erroneous.  When the approximate Q-function is initialized, if the effect of
actions on the Q-function is order of magnitudes higher than what it should be,
approximating $Q^\pi_\deltat$ is likely to be difficult. Besides, the error is likely
to be further propagated when the equation used to update our approximate $Q$
function relies on bootstraping, as is the case for usual temporal difference
derived methods.

In what follows, a discrete algorithm that has a well defined time continuous
limit is defined. The algorithm relies on three elements, namely, defining and
learning a quantity that contains some information on the hierarchy of actions
while admitting a time continuous limit, defining exploration methods that
admit a continuous time limit and defining learning rates that induce well
behaved parameter trajectories when $\deltat$ goes to $0$.

\subsection{Advantage Updating}
\label{subsec:reparam}
To define an object which contains the same information on actions as
$Q^\pi_\deltat$, but admits an action dependant continuous time limit, , it is
natural to define
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat},
    \label{eq:adv}
\end{align}
a rescaled version of the advantage function, as the difference between between
$Q^\pi_\deltat(s, a)$ and $V^\pi\deltat(s)$ is of order $\bigO(\deltat)$.
Contrary to the action state value function, the rescaled advantage function converges
to an action dependent quantity when $\deltat$ goes to $0$
\begin{align}
	A^\pi_\deltat(s, a)=&\reward(s, a)+\frac{\gamma^{\deltat}\E_{\delta s \sim \delta s(s, a)}V^\pi_\deltat(s + \delta s)-V^\pi\deltat(s)}{\deltat}\nonumber\\
	=&\reward(s, a)+(\gamma - 1) V^\pi(s)+\partial_s V^\pi(s)f(s, a)\nonumber\\
         &+\frac{\text{tr}\left(\Sigma^T(s, a)\partial^2_{s^2}V^\pi(s) \Sigma(s,a)\right)}{2} + O(\deltat)\nonumber.
\end{align}
The discretized state action value function can then be rewritten as
\begin{equation}
	Q^\pi_\deltat(s, a) = V^\pi_\deltat(s) + \deltat A^\pi_\deltat(s, a).
	\label{eq:reparam_q_pi}
\end{equation}
A natural way of approximating $V^\pi_\delta$ and $A^\pi_\deltat$ is to apply
\emph{Sarsa} or Q-learning to a reparameterized Q-function approximator
\begin{equation}
	Q_\theta(s, a) = V_{\theta_1}(s) + \deltat A_{\theta_2}(s, a).
\end{equation}
To avoid cumbersome notations, in what follows, parameter indices are dropped.
At initialization, if both $V_{\theta_1}$ and $A_{\theta_2}$ are initialized
independantly of $\deltat$, this parameterization reasonably scales the
contribution of actions relative to states in the value of $Q$.

However, the proposed reparameterization does not, on its own, guarantee that
when $Q$ correctly approximates $Q^\pi_\deltat$, $A$ approximates $A^\pi_\deltat$.
Indeed, for any given pair $V$, $A$,
\begin{align}
	\tilde{V}(s) &= V(s) - f(s)\\
	\tilde{A}(s, a) &= A(s, a) + \frac{f(s)}{\deltat}
\end{align}
yields the exact same $Q$ function. Consequently, $Q$ can correctly approximate
$Q^\pi$ even if $A$ is arbitrarily far from $A^\pi$.
To enforce, identifiability of $A$, one must enforce the consistency equation
\begin{equation}
	Q^\pi_\deltat(s, \pi(s)) - V^\pi_\deltat(s) = 0
\end{equation}
on the approximate $A$ and $V$. This translates to
\begin{equation}
	A(s, \pi(s)) = 0.
\end{equation}
With this additional constraint, if $Q^\pi_\deltat = Q$,
\begin{align}
	A^\pi_\deltat(s, a) &= \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat}\\
		    &= \frac{Q(s,a) - Q(s, \pi(s))}{\deltat}\\
		    &= A(s, a).
\end{align}
In the spirit of~\cite{dueling_nets}, this condition is enforced by writing $A$ as
\begin{equation}
	A(s, a) = \bar{A}(s, a) - \bar{A}(s, \pi(s)).
\end{equation}

### 2019-01-10 paper/icml_drau/framework.tex
Advances.

\section{Near continuous time reinforcement learning}
\label{sec:continous}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.
\TODO{. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.}

@@

As the difference between between $Q^\pi(s, a)$ and $V^\pi(s)$ is of order
$\bigO(\deltat)$, it is natural to define a rescaled version of the advantage
function, namely
\begin{align}
	A^\pi(s, a) &= \frac{Q^\pi(s,a) - V^\pi(s)}{\deltat}\\
		    &= \reward(s, a) +
		    \frac{\gamma^{\deltat} \E_{\delta s \sim \delta s(s, a)} V^\pi(s + \delta s) - V^\pi(s)}{\deltat}.
    \label{eq:adv}
\end{align}
Contrary to the action state value function, the rescaled advantage function converges
to an action dependent quantity when $\deltat$ goes to $0$
\begin{align}
	A^\pi(s, a) &\xrightarrow[\deltat \to 0]{} \reward(s, a) +
	(\gamma - 1) V^\pi(s) + \partial_s V^\pi(s) f(s, a)\nonumber\\
		    &+
	\frac{\text{tr}\left(\Sigma^T(s, a)\partial^2_{s^2}V^\pi(s) \Sigma(s,a)\right)}{2},
\end{align}
and $Q^\pi$ can then be rewritten as
\begin{equation}
	Q^\pi(s, a) = V^\pi(s) + \deltat A^\pi(s, a).
	\label{eq:reparam_q_pi}
\end{equation}

>>>>

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:framework}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.
\TODO{. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.}

@@
